Collocated Snapshot Backup with VM-Centric Deduplication in the Cloud

### 2013-09-23 snapshot_system/fast14_abstract.tex
revisions

\begin{abstract}
A cloud environment that hosts a large number of virtual machines (VMs) has
a high storage demand for frequent backup of system image snapshots and
signature-based deduplication of data blocks is necessary to eliminate excessive 
redundant blocks. Collocating a cluster-based duplicate service with other cloud services
reduces network traffic;
however it is resource expensive and less fault-resilient to perform global deduplication
and let a data block be shared by many virtual machines. 
This paper proposes a VM-centric collocated backup service that  
localizes deduplication as much as possible within each virtual machine using similarity-guided
search and associates  underlying file blocks with one VM for most cases.
It restricts cross-VM deduplication to popular blocks with extra replication support.
Our analysis shows that  this VM centric scheme 
can  provide  better fault tolerance while using a small amount of computing and storage resources. 
This  paper  describes a comparative evaluation of this scheme in  accomplishing a competitive deduplication 
efficiency while sustaining a good backup throughput. 
\end{abstract}

>>>>

\begin{abstract}
A cloud environment that hosts a large number of virtual machines (VMs) has
a high storage demand for frequent backup of system image snapshots. 
Deduplication of data blocks is necessary to eliminate
redundant blocks and reduce cost. Collocating a cluster-based duplicate service with other cloud services
reduces network traffic;
however, performng global deduplication and letting a data block be shared
by many virtual machines is resource expensive and less fault-resilient. 
This paper proposes a VM-centric collocated backup service that  
localizes deduplication as much as possible within each virtual machine using similarity-guided
search and associates  underlying file blocks with one VM for most cases.
It restricts cross-VM deduplication to popular blocks with extra replication support.
Our analysis shows that  this VM centric scheme 
can  provide  better fault tolerance while using a small amount of computing and storage resources. 
This  paper  describes a comparative evaluation of this scheme in  accomplishing a competitive deduplication 
efficiency while sustaining a good backup throughput. 
\end{abstract}

### 2013-09-23 snapshot_system/fast14_architecture.tex
revised evaluation etc
revisions

We use the virtual device driver in Xen that employs a bitmap to track the changes 
that have been made to virtual disk.
Every bit in the bitmap represents a fix-sized (2MB) region called a \textit{segment}, indicating whether the segment
has been modified since last backup. 
Segments are further divided into variable-sized chunks (average 4KB) 
using a content-based chunking algorithm~\cite{frame05}, 
which brings the opportunity of fine-grained deduplication.
When the VM issues a disk write, the dirty bit for the corresponding segment is set
and this indicates such a segments needs to be checked during snapshot backup. 
After the snapshot backup is finished, the driver resets the dirty bit map to a clean state.
For data modification during backup, a copy-on-write protection is set so that backup can continue to
copy  a specific version while new changes are still recorded.
%copies a frozen version while the modification can still carry on.

@@

\begin{figure*}[t]
    \centering
    \includegraphics[width=6in]{images/socc_arch_cluster}
    \caption{System Architecture}
    \label{fig:arch_vm}
\end{figure*}

@@

\begin{itemize}
\item Data of each VM snapshot store excluding PDS is divided into a set of containers and 
each container is approximately 1GB. 
The reason for dividing the snapshot into containers is to simplify the compaction process
conducted periodically. As discussed later, data chunks are deleted from old snapshots
and chunks without any reference from other snapshots can be removed by this compaction process.
By limiting the size of a container, we can effectively control the length of each round of compaction.
The compaction  routine can work on one container at a time and move the used data chunks to another container.

>>>>

We use the virtual device driver in Xen that employs a bitmap to track the changes 
that have been made to the virtual disk.
Every bit in the bitmap represents a fix-sized (2MB) region called a \textit{segment}, indicating whether the segment
has been modified since last backup. 
Segments are further divided into variable-sized chunks (average 4KB) 
using a content-based chunking algorithm~\cite{frame05}, 
which brings the opportunity of fine-grained deduplication.
When the VM issues a disk write, the dirty bit for the corresponding segment is set
and this indicates such a segments needs to be checked during snapshot backup. 
After the snapshot backup is finished, the driver resets the dirty bit map to a clean state.
For data modification during backup, a copy-on-write protection is set so that backup can continue to
copy  a specific version while new changes are still recorded.
%copies a frozen version while the modification can still carry on.

@@

\begin{figure*}[t]
    \centering
    \includegraphics[width=4.5in]{images/socc_arch_cluster}
    \caption{System Architecture}
    \label{fig:arch_vm}
\end{figure*}

@@

\begin{itemize}
\item Data of each VM snapshot store, excluding the PDS store, are divided into a set of containers and 
each container is approximately 1GB. 
The reason for dividing the snapshot into containers is to simplify the compaction process
conducted periodically. As discussed later, data chunks are deleted from old snapshots
and chunks without any reference from other snapshots can be removed by this compaction process.
By limiting the size of a container, we can effectively control the length of each round of compaction.
The compaction  routine can work on one container at a time and move the in-use data chunks to another container.

### 2013-09-23 snapshot_system/fast14_background.tex
revised evaluation
revisions

Our key design consideration is VM dependence minimization during deduplication and file block management.
\begin{itemize}
\item {\em Deduplication localization.}
Because a data chunk is compared with signatures collected from all VMs during
the deduplication process, only one copy of duplicates is stored in the storage,
this artificially creates data dependencies among different VM users. 
Content sharing via deduplication affects fault isolation since machine failures happen periodically 
in a large-scale cloud and
loss of a small number of shared data chunks can 
cause the unavailability of snapshots for a large number of virtual machines.
Localizing the impact of deduplication can increase fault isolation and resilience.
Thus from the fault tolerance point of view,  duplicate sharing among multiple VMs is 
discouraged. 
Another disadvantage of sharing is that it complicates snapshot deletion, 
which  occurs frequently when snapshots expire regularly. 
The mark-sweep approach~\cite{Guo2011} is effective for deletion, and its main cost
is to count if a data chunk is still shared by other snapshots.
Localizing deduplication can  minimize data sharing and simplify deletion while sacrificing 
deduplication efficiency, and  can faciltate parallel execition of snaptshot operations.
\item{\em  Management of file system blocks.}
The file block size in a distributed file system such as  Hadoop and GFS is uniform and large (e.g.  64MB),
 a data chunk in a typical deduplication system is of a nonuniform size with 4KB or 8KB on average.
Packaging data chunks to a file system block can create more data dependence among VMs
since a file block can be shared with even more VMs.
Thus we need to consider a minimum association of a fie system block to VMs in the packaging process.
\end{itemize}

Another consideration is the computing cost of deduplication.
Because of collocation of this snapshot service with other existing cloud services, 
cloud providers will want the backup service to only consume small resources
with a minimal impact to the existing cloud services.
The key resource for signature comparison  is memory for storing the fingerprints. 
We will consider the approximation techniques with less memory consumption along 
with the fault isolation consideration discussed below.

We call the traditional deduplication approach as   VM-oblivious (VO)
because they compare fingerprints of snapshots without consideration of VM.
With the above  considerations in mind, we study a 
VM-centric approach (called VC)
for a collocated backup service with resource usage friendly
to the existing applications.  
In designing a VC duplication algorithm, we have considered and adopted some of
the following previously-developed techniques.
\begin{itemize}
\item {\bf Version-based change detection}.
VM snapshots can be  backed up  incrementally by identifying file  blocks that have
changed from the previous version of the snapshot~\cite{Clements2009,Vrable2009,TanIPDPS2011}.
Such a scheme  is  VM-centric since deduplication is localized. 
We are seeking for a tradeoff since 
cross-VM  signature comparison can deliver additional compression~\cite{Guo2011,Dong2011,extreme_binning09}.
\item {\bf Stateless  Data Routing}.
One approach for scalable duplicate comparison is to use a content-based hash
partitioning algorithm called stateless data routing by Dong et al.~\cite{Dong2011} 
that divides the deduplication work with a similarity approximation. This work 
is similar to Extreme Binning by Bhagwat et al.~\cite{extreme_binning09} and 
each request is routed  to a machine which holds
a Bloom filter  or can fetch on-disk index for additional comparison.
While this approach is VM-oblivious, it motivates us to  use  a combined signature of a dataset to narrow
VM-specific local search.
\item {\bf Sampled Index}.
One effective approach that reduces memory usage is 
to use a sampled index with prefetching, proposed  by Guo and Efstathopoulos\cite{Guo2011}. 
The algorithm is VM oblivious and it is not easy  to adopt for a distributed architecture. 
To use a distributed memory version of the sampled index, every deduplication request
may access a remote machine for index lookup and the overall overhead of access latency for all requests
can be significant.  
\end{itemize}

>>>>

Our key design consideration is VM dependence minimization during deduplication and file block management.
\begin{itemize}
\item {\em Deduplication localization.}
Because a data chunk is compared with signatures collected from all VMs during
the deduplication process, only one copy of duplicates is stored in the storage,
this artificially creates data dependencies among different VM users. 
Content sharing via deduplication affects fault isolation since machine failures happen periodically 
in a large-scale cloud and
loss of a small number of shared data chunks can 
cause the unavailability of snapshots for a large number of virtual machines.
Localizing the impact of deduplication can increase fault isolation and resilience.
Thus from the fault tolerance point of view,  duplicate sharing among multiple VMs is 
discouraged. 
Another disadvantage of sharing is that it complicates snapshot deletion, 
which  occurs frequently when snapshots expire regularly. 
The mark-and-sweep approach~\cite{Guo2011} is effective for deletion, but has a high cost, and its main cost
is to count if a data chunk is still shared by other snapshots.
Localizing deduplication can  minimize data sharing and simplify deletion while sacrificing 
deduplication efficiency, and  can faciltate parallel execution of snaptshot operations.
\item{\em  Management of file system blocks.}
The file block size in a distributed file system such as  Hadoop and GFS is uniform and large (e.g.  64MB),
while the data chunk in a typical deduplication system is of a nonuniform size with 4KB or 8KB on average.
Packaging data chunks to a file system block can create more data dependencies among VMs
since a file block can be shared by even more VMs.
Thus we need to consider a minimum association of a fie system block to VMs in the packaging process.
\end{itemize}

Another consideration is the computing cost of deduplication.
Because of collocation of this snapshot service with other existing cloud services, 
cloud providers will want the backup service to only consume small resources
with a minimal impact to the existing cloud services.
The key resource for signature comparison  is memory for storing the fingerprints. 
We will consider the approximation techniques with reduced memory consumption along 
with the fault isolation considerations discussed below.

We call the traditional deduplication approach as   VM-oblivious (VO)
because they compare fingerprints of snapshots without consideration of VMs.
With the above  considerations in mind, we study a 
VM-centric approach (called VC)
for a collocated backup service with resource usage friendly
to the existing applications.

In designing a VC duplication algorithm, we have considered and adopted some of
the following previously-developed techniques.
1)
{\em Version-based change detection}.
VM snapshots can be  backed up  incrementally by identifying file  blocks that have
changed from the previous version of the snapshot~\cite{Clements2009,Vrable2009,TanIPDPS2011}.
Such a scheme  is  VM-centric since deduplication is localized. 
We are seeking for a tradeoff since 
cross-VM  signature comparison can deliver additional compression~\cite{Guo2011,Dong2011,extreme_binning09}.
2) {\em Stateless  data Routing}.
One approach for scalable duplicate comparison is to use a content-based hash
partitioning algorithm called stateless data routing by Dong et al.~\cite{Dong2011} 
that divides the deduplication work with a similarity approximation. This work 
is similar to Extreme Binning by Bhagwat et al.~\cite{extreme_binning09} and 
each request is routed  to a machine which holds
a Bloom filter  or can fetch on-disk index for additional comparison.
While this approach is VM-oblivious, it motivates us to  use  a combined signature of a dataset to narrow
VM-specific local search.
3) {\em Sampled Index}.
One effective approach that reduces memory usage is 
to use a sampled index with prefetching, proposed  by Guo and Efstathopoulos\cite{Guo2011}. 
The algorithm is VM oblivious and it is not easy  to adopt for a distributed architecture. 
To use a distributed memory version of the sampled index, every deduplication request
may access a remote machine for index lookup and the overall overhead of access latency for all requests
can be significant.

### 2013-09-23 snapshot_system/fast14_deduplication.tex
revisions

Since the best deduplication uses a nonuniform chunk size 
in the average of 4K or 8K~\cite{Jin2009},
we conduct additional local inner-VM deduplication on a snapshot by comparing
chunk fingerprints of a dirty segment 
with those in  {\em similar} segments from its parent snapshot. 
We define two segments are similar if their content signature is the same.
This segment content signature value is defined as the minimum value of all its chunk fingerprints 
computed during backup and is recorded in the snapshot metadata (called recipe). Note that this definition of
content similarity is  an approximation~\cite{AdnriBroader}.  When processing a dirty segment,
its  similar segments can be found easily from the
parent snapshot recipe.  Then recipes of the similar segments are loaded to memory,
which contain chunk fingerpints to be compared.
To control the time cost of search, we set a limit on the the number of  similar segments to be  fetched. 
% Then,
%given a set of data chunks within a dirty segment,  we compare  these chunk fingerprints
%with those in similar segments.  
For example, a 2MB segment contains about 500 fingerprints and by limiting at most 10 similar
segments to search, the amount of memory for maintaining those fingerprints in similar segments is small.

@@

\begin{figure}
\centering
%\epsfig{file=log-log.disk,width=3in}
%source ../vm_snapshot_sim/images/log-log.disk.eps
 \includegraphics[width=3in]{figures/log-log-disk}
\caption{Duplicate frequency versus  chunk ranking in a log scale after inner-VM deduplication.}
\label{fig:Datazipf}
\end{figure}
We have not  adopted the  sampled index~\cite{Guo2011} 
for  detecting duplicates from popular chunks.
For the data sets we have tested, the spatial locality 
among popular
data chunks is limited and  on average the number of consecutive data chunks is 7 among popular chunks.
This is not sufficient to enable prefetching which is required  for index sampling.

@@

% {\it [Need to find a place to put these numbers in: Total number of chunks 
% in 350 snapshots: 1,546,635,485. 
% Total number of chunks after localized dedup: 283,121,924. Total number of unique chunks: 87,692,682.]}
\subsection{Impact on deduplication efficiency}
Choosing the value  $k$ for the most popular chunks affects the deduplication efficiency.
We analyze this impact based on the characteristics  of the VM snapshot traces
studied from  application datasets.
Our previous study shows that the popularity of data chunks after inner VM deduplication follows 
a Zipf-like distribution\cite{Breslau1999a} and its
exponent $\alpha$ is ranged between 0.65  and  0.7~\cite{WeiZhangIEEE}. 
Figure~\ref{fig:Datazipf} illustrates the Zipf-like distribution of chunk popularity.
We will use a number of parameters in our analysis below and they are defined in
Table~\ref{tab:symbol}.

@@

\begin{figure}[htbp]
  \centering
    \begin{tikzpicture}
            \begin{axis}[
            %title={PDS Coverage},
            width=\linewidth,
            height=0.6\linewidth,
            cycle multi list={
                mline\nextlist
                [3 of]mmark*\nextlist
            },
            %cycle list name=mcolor,
            xlabel={Total num. chunks stored (in billions)},
            ylabel={PDS Coverage (\%)},
            %extra y ticks={4.5,5.5,6.5} %to add extra ticks
            mark options=solid,
            %legend pos=outer north east,
            legend columns=2,
            legend style={
                at={(0.5,-0.30)},
            anchor=north},
            ]
            \addplot table[x expr=\thisrow{InputChunks}/1000000000,y=A1] {figures/cds_coverage.txt};
            \addplot table[x expr=\thisrow{InputChunks}/1000000000,y=A2] {figures/cds_coverage.txt};
            \addplot table[x expr=\thisrow{InputChunks}/1000000000,y=A4] {figures/cds_coverage.txt};
            \addplot table[x expr=\thisrow{InputChunks}/1000000000,y=T1] {figures/cds_coverage.txt};
            \addplot table[x expr=\thisrow{InputChunks}/1000000000,y=T2] {figures/cds_coverage.txt};
            \addplot table[x expr=\thisrow{InputChunks}/1000000000,y=T4] {figures/cds_coverage.txt};
            \legend{Measured ($\sigma=1\%$),Measured ($\sigma=2\%$),Measured ($\sigma=4\%$),Predicted ($\sigma=1\%$),Predicted ($\sigma=2\%$),Predicted ($\sigma=4\%$)};
            \end{axis}
    \end{tikzpicture}
  \caption{Predicted vs. actual PDS coverage as data size increases.}
  \label{fig:cds-coverage}
\end{figure}
Ratio $\sigma^{1-\alpha}$ represents the percentage of the remaining
chunks detected as duplicates in global cross-VM deduplication due to PDS.
We call this PDS coverage.
Figure~\ref{fig:cds-coverage} shows predicted PDS coverage using $\sigma^{1-\alpha}$ when $\alpha$ is fixed at
0.65 and measured PDS coverage in our test dataset.
$\sigma=2\%$ represents memory usage of approximately 100MB memory per machine for top $k$ PDS.
While the predicted value remains flat, the  real coverage actually increases as the data size
increases, which indicates that $\alpha$ increases with the data size. 
Thus in practice, the coverage of the PDS increases as more VMs are involved.

@@

Next we  assess  the impact of losing $d$ machines 
to the the VC and VO approaches.  
A large $\frac{r_c}{r}$ ratio can have a positive impact on full availability of VM snapshot blocks.
We use file system blocks rather than a deduplication
data chunk as our unit of failure because the DFS keeps
filesystem blocks as its base unit of storage.
To compute the full availability of all snapshots of a VM, we derive
the probablity of losing a snapshot file block of a VM by
estimating the number of file system blocks per VM in each approach.
As illustrated in Figure~\ref{fig:share},
we build a bipartite graph representing the association from unique file system blocks
to their corresponding VMs in each approach. An association edge is  drawn  from a file block  to a VM 
if this block is used by this VM.

@@

Thus $N_1$ is much smaller than $N_o$. 
When there is a failure in file blocks with replication degree $r$
and there is no failure for PDS data with more replicas,   a VM in
the VC approach has a much lower chance to lose a snapshot than VO. 
%Figure~\ref{fig:fsb-links} shows the average number of VMs sharing each file block from
%our test dataset.
%For VC, we only show
%the sharing degree of  PDS-oriented file blocs  because non-PDS blocks always belong to
%one VM.
%Figure~\ref{fig:fsb-links} shows the average number of VMs sharing each file block from our test data.
Figure~\ref{fig:vm-links} shows the average number of file system blocks for each VM in VC and in VO. 
From data, we have observed that $N_1 +N_2 < N_o$ in practice. 
This is likely because the PDS FSBs tightly pack data used by many VMs, 
which decreases the overall number of FSBs required to backup a VM.
Noted that  if  the backup for multiple VMs were conducted concurrently, there would be more
VMs shared  by each file block on average in VO.

@@

\begin{table}
    \footnotesize
    \tabcolsep=0.11cm
    \begin{tabular}{|l|l|l|l|}
        \hline
        \multirow{2}{*}{Failures}   & \multicolumn{3}{c|}{FSB Availability} \\
                                    %\cline{2-4}
                                    & $R_c=3$ & $R_c=6$ & $R_c=9$ \\
        \hline
        3 & 99.999 & 100 & 100\\
        5 & 99.994 & 100 & 100\\
        10 & 99.925 & 99.999 & 99.999\\
        20 & 99.295 & 99.997 & 99.999 \\
        \hline
    \end{tabular}
    \caption{Availability of individual 64MB Filesystem blocks (FSBs) as storage
    nodes fail in a 100 node cluster.}
    \label{tab:fsb-availability}
\end{table}

>>>>

Since the best deduplication uses a nonuniform chunk size 
in the average of 4K or 8K~\cite{Jin2009},
we conduct additional local inner-VM deduplication on a snapshot by comparing
chunk fingerprints of a dirty segment 
with those in  {\em similar} segments from its parent snapshot. 
We define two segments are similar if their content signature is the same.
This segment content signature value is defined as the minimum value of all its chunk fingerprints 
computed during backup and is recorded in the snapshot metadata (called recipe). Note that this definition of
content similarity is  an approximation~\cite{AdnriBroader}.  When processing a dirty segment,
its  similar segments can be found easily from the
parent snapshot recipe.  Then recipes of the similar segments are loaded to memory,
which contain chunk fingerpints to be compared.
To control the time cost of search, we set a limit on the the number of  similar segments to be  fetched. 
% Then,
%given a set of data chunks within a dirty segment,  we compare  these chunk fingerprints
%with those in similar segments.  
For example, a 2MB segment contains about 500 fingerprints and by limiting at most 10 similar
segments to search, the amount of memory for maintaining those fingerprints in similar segments is small.
As part of our local duplicate search we also compare the current segment
against the parent segment at the same offset.

@@

\begin{figure}
\centering
%\epsfig{file=log-log.disk,width=3in}
%source ../vm_snapshot_sim/images/log-log.disk.eps
 \includegraphics[width=3in]{figures/log-log-disk}
\caption{Duplicate frequency versus  chunk ranking in a log scale after inner-VM deduplication.}
\label{fig:Datazipf}
\end{figure}
We have not  adopted the  sampled index~\cite{Guo2011} 
for  detecting duplicates from popular chunks.
For the data sets we have tested, the spatial locality 
among popular
data chunks is limited and  on average the number of consecutive data chunks is 7 among popular chunks.
This is not sufficient to enable effective prefetching which is required  for index sampling.

@@

% {\it [Need to find a place to put these numbers in: Total number of chunks 
% in 350 snapshots: 1,546,635,485. 
% Total number of chunks after localized dedup: 283,121,924. Total number of unique chunks: 87,692,682.]}
\subsection{Impact on deduplication efficiency}
Choosing the value  $k$ for the most popular chunks affects the deduplication efficiency.
We analyze this impact based on the characteristics  of the VM snapshot traces
studied from  application datasets.
A previous study shows that the popularity of data chunks after inner VM deduplication follows 
a Zipf-like distribution\cite{Breslau1999a} and its
exponent $\alpha$ is ranged between 0.65  and  0.7~\cite{WeiZhangIEEE}. 
Figure~\ref{fig:Datazipf} illustrates the Zipf-like distribution of chunk popularity.
The parameters we will use in our analysis below are defined in
Table~\ref{tab:symbol}.

@@

\begin{figure}[htbp]
  \centering
    \begin{tikzpicture}
            \begin{axis}[
            %title={PDS Coverage},
            width=\linewidth,
            height=0.6\linewidth,
            cycle multi list={
                mline\nextlist
                [3 of]mmark*\nextlist
            },
            %cycle list name=mcolor,
            xlabel={Total num. chunks stored (in billions)},
            ylabel={PDS Coverage (\%)},
            %extra y ticks={4.5,5.5,6.5} %to add extra ticks
            mark options=solid,
            %legend pos=outer north east,
            legend columns=2,
            legend style={
                at={(0.5,-0.30)},
            anchor=north},
            ]
            \addplot table[x expr=\thisrow{InputChunks}/1000000000,y=A1] {figures/cds_coverage.txt};
            \addplot table[x expr=\thisrow{InputChunks}/1000000000,y=A2] {figures/cds_coverage.txt};
            \addplot table[x expr=\thisrow{InputChunks}/1000000000,y=A4] {figures/cds_coverage.txt};
            \addplot table[x expr=\thisrow{InputChunks}/1000000000,y=T1] {figures/cds_coverage.txt};
            \addplot table[x expr=\thisrow{InputChunks}/1000000000,y=T2] {figures/cds_coverage.txt};
            \addplot table[x expr=\thisrow{InputChunks}/1000000000,y=T4] {figures/cds_coverage.txt};
            \legend{Measured ($\sigma=1\%$),Measured ($\sigma=2\%$),Measured ($\sigma=4\%$),Predicted ($\sigma=1\%$),Predicted ($\sigma=2\%$),Predicted ($\sigma=4\%$)};
            \end{axis}
    \end{tikzpicture}
  \caption{Predicted vs. actual PDS coverage as data size increases.}
  \label{fig:cds-coverage}
\end{figure}
Ratio $\sigma^{1-\alpha}$ represents the percentage of the remaining
chunks detected as duplicates in global cross-VM deduplication due to PDS.
We call this PDS coverage.
Figure~\ref{fig:cds-coverage} shows predicted PDS coverage using $\sigma^{1-\alpha}$ when $\alpha$ is fixed at
0.65 and measured PDS coverage in our test dataset.
$\sigma=2\%$ represents memory usage of approximately 100MB memory per machine for the PDS.
While the predicted value remains flat, the  real coverage actually increases as the data size
increases, which indicates that $\alpha$ increases with the data size. 
Thus in practice, the coverage of the PDS increases as more VMs are involved.

@@

Next we  assess  the impact of losing $d$ machines 
to the the VC and VO approaches.  
A large $\frac{r_c}{r}$ ratio can have a positive impact on full availability of VM snapshot blocks.
We use file system blocks rather than a deduplication
data chunk as our unit of failure because the DFS keeps
filesystem blocks as its base unit of storage.
To compute the full availability of all snapshots of a VM, we derive
the probablity of losing a snapshot file block of a VM by
estimating the number of file system blocks per VM in each approach.
As illustrated in Figure~\ref{fig:share},
we build a bipartite graph representing the association from unique file system blocks
to their corresponding VMs in each approach. An association edge is  drawn  from a file block  to a VM 
if this block is used by the VM.

@@

Thus $N_1$ is much smaller than $N_o$. 
When there is a failure in file blocks with replication degree $r$
and there is no failure for PDS data with more replicas,   a VM in
the VC approach has a much lower chance to lose a snapshot than VO. 
%Figure~\ref{fig:fsb-links} shows the average number of VMs sharing each file block from
%our test dataset.
%For VC, we only show
%the sharing degree of  PDS-oriented file blocs  because non-PDS blocks always belong to
%one VM.
%Figure~\ref{fig:fsb-links} shows the average number of VMs sharing each file block from our test data.
Figure~\ref{fig:vm-links} shows the average number of file system blocks for each VM in VC and in VO. 
From data, we have observed that $N_1 +N_2 < N_o$ in practice. 
This is likely because the PDS FSBs tightly pack data used by many VMs, 
which decreases the overall number of FSBs required to backup a VM.
Note that  if  the backup for multiple VMs were conducted concurrently, there could be many more
VMs sharing each file block on average in VO.

@@

\begin{table}
    \footnotesize
    \tabcolsep=0.11cm
    \begin{tabular}{|l|l|l|l|}
        \hline
        \multirow{2}{*}{Failures}   & \multicolumn{3}{c|}{FSB Availability} \\
                                    %\cline{2-4}
                                    & $R=3$ & $R=6$ & $R=9$ \\
        \hline
        3 & 99.9994 & 100 & 100\\
        5 & 99.9939 & 100 & 100\\
        10 & 99.9258 & 99.9999 & 99.9999 \\
        20 & 99.2950 & 99.9967 & 99.9999 \\
        \hline
    \end{tabular}
    \caption{Availability of individual 64MB Filesystem blocks (FSBs) as storage
    nodes fail in a 100 node cluster.}
    \label{tab:fsb-availability}
\end{table}

### 2013-09-23 snapshot_system/fast14_introduction.tex
revisions

This paper seeks for a low-cost architecture option  that collocates
a backup service with other cloud services and  uses a minimum amount of resources. 
We also consider the fact that after
deduplication, most data chunks are shared by several to many virtual machines.
Failure of few shared data chunks can have a 
broad effect and many
snapshots of virtual machines could be affected.
The previous work in deduplication focuses on the efficiency and approximation of
fingerprint comparison, and has not addressed fault tolerance issues  together with deduplication.
Thus we also seek deduplication options that yield better fault isolation.
Another issue considered is that
that deletion of old snapshots competes for computing resource as well. 
Sharing of data chunks among by multiple VMs needs to be detected during
snapshot   deletion and such dependencies complicate deletion operations.

>>>>

This paper seeks for a low-cost architecture option  that collocates
a backup service with other cloud services and  uses a minimum amount of resources. 
We also consider the fact that after
deduplication, most data chunks are shared by several to many virtual machines.
Failure of a few shared data chunks can have a 
broad effect and many
snapshots of virtual machines could be affected.
The previous work in deduplication focuses on the efficiency and approximation of
fingerprint comparison, and has not addressed fault tolerance issues  together with deduplication.
Thus we also seek deduplication options that yield better fault isolation.
Another issue considered is that
that deletion of old snapshots also competes for computing resources. 
Sharing of data chunks among by multiple VMs needs to be detected during
snapshot   deletion and such dependencies complicate deletion operations.
